Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-02-15 WSSSPE2_report/WSSSPE2_review.tex
Minor changes to affiliations

\begin{xtabular}{ll}
Jordan Adams & Tulane University\\
Alice Allen & Astrophysics Source Code Library (ASCL)\\
Gabrielle Allen & U Illinois\\
Pierre-Yves Aquilanti & TOTAL E\&P R\&T USA\\
Wolfgang Bangerth\\
David Bernholdt & Oak Ridge National Laboratory\\
Jakob Blomer\\
Carl Boettiger & UCSC/ropensci\\
Chris Bogart & ISR/CMU\\
Steven R. Brandt & Louisiana State University\\
Tom Clune & NASA GSFC - \\
John W. Cobb\\
Dirk Colbry & Michigan State University\\
Karen Cranston & NESCent\\
Tom Crick & Cardiff Metropolitan University, UK\\
Ethan Davis & UCAR Unidata\\
Robert R Downs & CIESIN, Columbia University\\
Anshu Dubey & Lawrence Berkeley National Laboratory\\
Nicole Gasparini & Tulane University, New Orleans\\
Yolanda Gil & Information Sciences Institute, University of Southern California\\
Kurt Glaesemann & Pacific northwest national lab\\
Sol Greenspan &  National Science Foundation\\
Ted Habermann & The HDF Group\\
Marcus D. Hanwell & Kitware\\
Sarah Harris & University of Leeds\\
David Henty &  EPCC, The University of Edinburgh\\
Neil Chue Hong & Software Sustainability Institute \& University of Edinburgh\\
James Howison & University of Texas\\
Maxime Hughes\\
Eric Hutton &  University of Colorado\\
Ray Idaszak & RENCI/UNC\\
Samin Ishtiaq & Microsoft Research Cambridge, UK\\
Matt Jones &  University of California Santa Barbara\\
Nick Jones & New Zealand eScience Infrastructure, University of Auckland\\
Daniel S. Katz & U Chicago \& Argonne\\
Ian Kelley\\
Hilmar Lapp & National Evolutionary Synthesis Center (NESCent) and Duke University\\
Chris Lenhardt\\
Richard Littauer & MIT/University of Saarland \\
Frank L\"{o}ffler & Louisiana State University\\
Andre Luckow & Rutgers\\
Berkin Malkoc & Istanbul Technical University\\
Kyle Marcus & University of Buffalo\\
Bryan Marker & The University of Texas at Austin\\
Suresh Marru & Indiana University \\
Robert H. McDonald & Indiana University - Data to Insight Center/Libraries - \\
Rupert Nash\\
Andy Nutter-Upham & Whitehead Institute\\
Abani Patra & Univ @ Buffalo\\
Aleksandra Pawlik & Software Sustainability Institute\\
Cody J. Permann & Idaho National Laboratory\\
John W. Peterson & Idaho National Laboratory\\
Benjamin Pharr & University of Mississippi\\
Stephen Piccolo &  Brigham Young University, Utah\\
Marlon Pierce & Indiana University\\
Ray Plante & NCSA/University of Illinois Urbana-Champaign\\
Sushil Prasad & Georgia State University, Atlanta \\
Karthik Ram & University of California, Berkeley. Berkeley Institute for Data Science and rOpenSci\\
Mike Rilee\\
Mike Rilee & NASA/GSFC, Rilee Systems Technologies - \\
Erin Robinson & Foundation for Earth Science \\
Mark Schildhauer &  NCEAS, Univ. Calif, Santa Barbara\\
Jory Schossau & Michigan State University\\
Frank Seinstra & Netherlands eScience Center\\
James Shepherd & Rice University\\
Justin Shi\\
Ardita Shkurti & University of Nottingham\\
Alan Simpson &  EPCC, The University of Edinburgh\\
Carol Song & Purdue University\\
James Spencer & Imperial College London\\
Tracy Teal & Data Carpentry\\
Kaitlin Thaney &  Mozilla Science Lab\\
Matt Turk & NCSA/UIUC\\
Colin C. Venters & University of Huddersfield\\
Nathan Weeks\\
Ethan White & University of Florida/Utah State University\\
Nancy Wilkins-Diehr & SDSC\\
Greg Wilson &  Software Carpentry\\
\end{xtabular}

>>>>

\begin{xtabular}{ll}
Jordan Adams & Tulane University\\
Alice Allen & Astrophysics Source Code Library (ASCL)\\
Gabrielle Allen & U Illinois\\
Pierre-Yves Aquilanti & TOTAL E\&P R\&T USA\\
Wolfgang Bangerth\\
David Bernholdt & Oak Ridge National Laboratory\\
Jakob Blomer\\
Carl Boettiger & UCSC/ropensci\\
Chris Bogart & ISR/CMU\\
Steven R. Brandt & Louisiana State University\\
Tom Clune & NASA GSFC\\
John W. Cobb\\
Dirk Colbry & Michigan State University\\
Karen Cranston & NESCent\\
Tom Crick & Cardiff Metropolitan University, UK\\
Ethan Davis & UCAR Unidata\\
Robert R Downs & CIESIN, Columbia University\\
Anshu Dubey & Lawrence Berkeley National Laboratory\\
Nicole Gasparini & Tulane University, New Orleans\\
Yolanda Gil & Information Sciences Institute, University of Southern California\\
Kurt Glaesemann & Pacific northwest national lab\\
Sol Greenspan &  National Science Foundation\\
Ted Habermann & The HDF Group\\
Marcus D. Hanwell & Kitware\\
Sarah Harris & University of Leeds\\
David Henty &  EPCC, The University of Edinburgh\\
Neil Chue Hong & Software Sustainability Institute \& University of Edinburgh\\
James Howison & University of Texas\\
Maxime Hughes\\
Eric Hutton &  University of Colorado\\
Ray Idaszak & RENCI/UNC\\
Samin Ishtiaq & Microsoft Research Cambridge, UK\\
Matt Jones &  University of California Santa Barbara\\
Nick Jones & New Zealand eScience Infrastructure, University of Auckland\\
Daniel S. Katz & U Chicago \& Argonne\\
Ian Kelley\\
Hilmar Lapp & National Evolutionary Synthesis Center (NESCent) and Duke University\\
Chris Lenhardt\\
Richard Littauer & MIT/University of Saarland \\
Frank L\"{o}ffler & Louisiana State University\\
Andre Luckow & Rutgers\\
Berkin Malkoc & Istanbul Technical University\\
Kyle Marcus & University of Buffalo\\
Bryan Marker & The University of Texas at Austin\\
Suresh Marru & Indiana University \\
Robert H. McDonald & Indiana University - Data to Insight Center/Libraries \\
Rupert Nash\\
Andy Nutter-Upham & Whitehead Institute\\
Abani Patra & Univ @ Buffalo\\
Aleksandra Pawlik & Software Sustainability Institute\\
Cody J. Permann & Idaho National Laboratory\\
John W. Peterson & Idaho National Laboratory\\
Benjamin Pharr & University of Mississippi\\
Stephen Piccolo &  Brigham Young University, Utah\\
Marlon Pierce & Indiana University\\
Ray Plante & NCSA/University of Illinois Urbana-Champaign\\
Sushil Prasad & Georgia State University, Atlanta \\
Karthik Ram & University of California, Berkeley. Berkeley Institute for Data Science and rOpenSci\\
Mike Rilee\\
Mike Rilee & NASA/GSFC, Rilee Systems Technologies \\
Erin Robinson & Foundation for Earth Science \\
Mark Schildhauer &  NCEAS, Univ. California, Santa Barbara\\
Jory Schossau & Michigan State University\\
Frank Seinstra & Netherlands eScience Center\\
James Shepherd & Rice University\\
Justin Shi\\
Ardita Shkurti & University of Nottingham\\
Alan Simpson &  EPCC, The University of Edinburgh\\
Carol Song & Purdue University\\
James Spencer & Imperial College London\\
Tracy Teal & Data Carpentry\\
Kaitlin Thaney &  Mozilla Science Lab\\
Matt Turk & NCSA/UIUC\\
Colin C. Venters & University of Huddersfield\\
Nathan Weeks\\
Ethan White & University of Florida/Utah State University\\
Nancy Wilkins-Diehr & SDSC\\
Greg Wilson &  Software Carpentry\\
\end{xtabular}
